VOI-aware Monte Carlo Sampling in Trees

### 2011-12-08 paper/vago/paper.tex
Go: introduction

Figure~\ref{fig:random-instances} shows experiment results for
randomly-generated multi-armed bandits with 32 Bernoulli arms, with
the mean rewards of the arms distributed uniformly in the range $[0,
  1]$, for a range of sample budgets $32..2048$, with multiplicative
step of $2$. The experiment for each number of samples was repeated
20000 times. UCT is worse than any of the VOI-aware sampling policies,
for example, for 384 samples the simple regret of UCT is $\approx 40$
times greater than of VCT, and $\approx 100$ times greater than of
ECT. On average, it takes $2.5$ times as many samples for UCT to reach
the regret of VCT.

@@

>>>>

Figure~\ref{fig:random-instances} shows experiment results for
randomly-generated multi-armed bandits with 32 Bernoulli arms, with
the mean rewards of the arms distributed uniformly in the range $[0,
  1]$, for a range of sample budgets $32..2048$, with multiplicative
step of $2$. The experiment for each number of samples was repeated
20000 times. UCT is worse than any of the VOI-aware sampling policies,
for example, for 384 samples the simple regret of UCT is $\approx 40$
times greater than of VCT, and $\approx 100$ times greater than of
ECT. On average, it takes $2.5$ times as many samples for UCT to reach
the regret of VCT. Different numbers of arms and distributions of
means give similar results.

@@

One search domain in which Monte-Carlo tree search based on the UCT
sampling policy has been particularly successful is playing the Go
game \cite{Gelly.mogo}. This series of experiments compares
the winning rate of VOI-aware policies (VCT, ECT, BCT) against UCT 
in Go and investigates the effect of early stopping and sample
redistribution.

For the experiments, a modified version of Pachi \cite{Braudis.pachi},
a state of the art Go program, was used:
\begin{itemize}
\item The UCT engine of Pachi was extended with VOI-aware sampling
  policies at the first step. 
\item The stopping condition for the VOI-aware policies was
  modified and based solely on the sample cost, specified as
  a constant parameter. 
\item The time-allocation mode based on the fixed number of samples
  was modified such that 
  \begin{enumerate}
    \item the same number of samples is available to
      the agent at each step, independently of the number of pre-simulated
      games;  
    \item if samples were unused at the current step,
      they become available at the next step.
  \end{enumerate}
\end{itemize}
